Analysis plan

### 2023-02-09 02. Design/MSG-P2312-Analysis Plan-2-sequence.rmd
Update MSG-P2312-Analysis Plan-2-sequence.rmd

We will use Daily Check-In data obtained from Management Science and
Innovation (MSI), a firm contracted to collect and maintain these data.
We will merge in additional variables from the GSA Roster obtained from
D2D. The GSA roster is updated monthly at the end of each month. [We
currently have Nov 2022 and Dec 2022 updates; I will try to track down
past months. Ideally, we will merge in each monthly check-in file with
the preceding month's roster file.]

@@

For cluster analysis of staff work status, the data will be transformed
so that each row is one staff person. From the raw data, the following
variables will be defined:

>>>>

We will use Daily Check-In data obtained from Management Science and
Innovation (MSI), a firm contracted to collect and maintain these data.
We will merge in additional variables from the GSA Roster obtained from
D2D. The GSA roster is updated monthly at the end of each month.

@@

For cluster analysis of staff work status, the data will be transformed
so that each row is one employee. From the raw data, the following
variables will be defined:
